A Meta-analysis of Fungicide Spray Schedules to Minimise Yield Loss from Powdery Mildew in Australian Mungbean

### 2020-08-07 paper/paper.Rmd
Fix space in colname of Table 2

```{r Table2, echo=FALSE}
data.frame(
  Scale = 1:9,
  `Scale Description` = c(
    "No sign of powdery mildew",
    "Small colonies in lower 1/3 of the canopy, up to 75% of the plants affected",
    "Colonies in lower 1/2 of the canopy, > 75% of the plants affected",
    "Colonies in lower 2/3 of the canopy, up to 75% of the plants affected",
    "Colonies in lower 2/3 of the canopy, > 75% of the plants affected",
    "Colonies in lower 2/3 of the canopy, 100% of the plants affected",
    "Colonies in lower 2/3 of the canopy, 100% of plants, with some plants with colonies in the top 1/3 of the canopy",
    "Colonies to top of the plant with > 75% of the plants affected",
    "Colonies to top of the plant with > 100% of the plants affected and heavy leaf drop"
  )
) %>%
  kable(format = "latex",
        booktabs = TRUE,
        caption = "Powdery mildew severity scoring scale.") %>%
  kable_styling()
```

>>>>

```{r Table2, echo=FALSE}
data.frame(
  Scale = 1:9,
  `Scale Description` = c(
    "No sign of powdery mildew",
    "Small colonies in lower 1/3 of the canopy, up to 75% of the plants affected",
    "Colonies in lower 1/2 of the canopy, > 75% of the plants affected",
    "Colonies in lower 2/3 of the canopy, up to 75% of the plants affected",
    "Colonies in lower 2/3 of the canopy, > 75% of the plants affected",
    "Colonies in lower 2/3 of the canopy, 100% of the plants affected",
    "Colonies in lower 2/3 of the canopy, 100% of plants, with some plants with colonies in the top 1/3 of the canopy",
    "Colonies to top of the plant with > 75% of the plants affected",
    "Colonies to top of the plant with > 100% of the plants affected and heavy leaf drop"
  )
) %>%
  kable(format = "latex",
        booktabs = TRUE,
        caption = "Powdery mildew severity scoring scale.",
        col.names = c("Scale",
                      "Scale Description")) %>%
  kable_styling()
```
